Recurrent Neural Networks for video object detection

### 2019-07-31 Paper/Paper_First_Draft.tex
Section based References

\begin{figure} [h]
\includegraphics[width=\columnwidth]{RMFSSD}
\caption{Architecture: Recurent Multi-frame single shot detector [1]. The Feature Extractor generates feature maps for four frames and feeds those feature maps into the GRUs. The Detection Head uses the final feature maps which are created by the GRU with respect to the temporal context to create Bounding Boxes and Class probabilities}
\end{figure}

In addition Broad, Jones and Lee test different types of SSDs as a baseline for their architecture. For all baseline SSDs the mAP was higher in comparison to the non-recurrent models. The mAP increase by 1.4 to 4.4 percent on KITTI dataset.  The best mAP is made with SqueezeDet+ \cite{b23} as a baseline SSD network [1-4.2].  \newline

@@

Afterwards, they compare LSTMs, GRUs and Bottleneck LSTMs by placing them after the 13th convolutional layer. Bottleneck-LSTMs have been designed by Liu and Zhu to increase the efficiency of LSTMs. They use ReLU as activation function and feed Bottleneck feature map with less input channel then the original feature map into the LST. They come to the conclusion that Bottleneck-LSTMs are more effective the LSTMs and in the case of a convolutional kernel greater 1x1 even more effective than GRUs while attaining comparable perfomance. [2-3.4; 2-4.2]\newline

@@

As shown in Fig. 2 the final model uses LSTMs after all feature maps, because Liu and Zhu observe that there is a slight performance improve by adding LSTMs after every feature map and nearly no change in computational cost [2-4.2].

\begin{figure} [h]
\includegraphics[width=\columnwidth]{Liu_Zhu}
\caption{Architecture Mobile Video Object Detection with temporally aware feature maps \cite{b2}. First 13 Convolutional Layeer create Feature Maps. Those Feature Maps are fed into the Bottleneck-LSTMs (faster LSTMs). Afterwards Convolutional-Layer create new Feature Maps and feed them again into Bottleneck-LSTMs.}
\end{figure}

@@

\subsection{Context Matters: Refining Object Detection in Video with Recurrent Neural Networks \cite{b4}}
In \cite{b4} Tripathi's, Lipton's, Belongie's and Nguyen's architecture consists two parts: A pseudo-labeler, which assigns labels to all video frames and a recurrent unit which refines those pseudo-labels by using the contextual information. Moreover, they describe a training strategy for their architecture and compare their approach to other models on the YouTube-Objects dataset (v2.0), which consists of the ten categories airplane, bird, boat, car, cow, dog, horse, mbike, train. Their model reaches an mAP of 68.73 percent which improves the strongest image-based baseline for Youtube-Video Objects dataset of 7.1\% [4-Abstract; 25]. \newline

@@

\begin{figure} [h]
\includegraphics[width=\columnwidth]{ContextMatters}
\caption{Architecture Context Matters: Refining Object Detection in Video with Recurrent Neural Networks \cite{b4}. First the "Pseudolabler" creates bounding boxes and class probabilities for every input frame. Afterwards the GRU fuses the output of the current and some past frames and refines the bounding boxes and class probabilities.}
\end{figure}

@@

\subsection{Spatially Supervised Recurrent Convolutional Neural Networks for Visual Object Tracking \cite{b5}}
Ning, Zhang, Huang, He, Ren and Wang design in \cite{b5} a combination of box-level and feature-level based Video detectors. They use the YOLO \cite{b27} network to create high-level visual features and preliminary location inferences and feed both into a recurrent unit. They test their approach on the OTB-30 dataset \cite{b28} and compared it with 9 different state-of-the-art trackers and outperform all of them. Their architecture, called ROLO, is shown in \textbf{figure}. [5-Abstract; 5-4]

@@

The architecture consists two main parts. The YOLO \cite{27} networks which collects visual features and outputs also preliminary location inferences and the LSTM which is used as a tracking module [5-2]. \newline

@@

In the pre-training phase convolutional layers, which create feature maps are pretrained on ImageNet data. Afterwards the YOLO-architecture is adopted as detection module and trained by using the traditional YOLO training phase. Last they add LSTMs for tracking. The LSTMs are fed with, the feature representations from the convolutional layers, the Bounding boxes from the detection module and the output states from the LSTM in the previous time-step. For training they use the Mean Squared Error (MSE) [5-3]: \newline

@@

In 2015 Wu, Lim and Yang published a comparison of different online object trackers on their one data set \cite{b28}. The best 9 architectures (STRUCK; CXT; OAB; CSK; VTD; VTS; LSK; TLD; RS) were used by Ning, Zhang, Huang, He, Ren and Wang to compare them with their own architecture. They use 30 videos with different objects (e.g.: car, human, Skater, Couple,..) out of the benchmark \cite{b28} dataset. They get the best tracking result in 13 videos and the second best in 3 videos. There is no other tracker that reaches the best results in more then 4 videos. \newline

@@

\subsection{Deep Feature Flow for Video Recognition \cite{2}}
Zhu, Xiong, Dai, Yuan and Wei develop in \cite{b2} a way to use flow nets to detect objects in video frames. As shown in figure 10 their architecture consists of three main parts: A network to create visual features, a network to create class probabilities and bounding boxes respectively the segmentation out of feature maps, and a network which estimates the optical flow. They tested their approach on the Cityscapes dataset with scenes for autonomous driving and ground-truth for semantic segmentation and the ImageNet VID dataset \cite{b35} with ground truth for object detection.

\begin{figure} [h]
\includegraphics[width=\columnwidth]{Flow}
\caption{Architecture Deep Feature Flow for Video Recognition}
\end{figure}

The paper differs between key frames and other frames. The network to create visual features $ N_{feat} $ only processes on key frames. It is a fully convolutional network, which takes as an input the image and outputs a feature maps. As a feature network they use a pretrained version of ResNet. \newline

The second network $ N_{task} $ does the recognition task over the feature maps. It performs on every frame.  Zhu, Xiong, Dai, Yuan and Wei use an R-FCN network for the recognition task.  \newline

For all non-key frames the feature maps are not constructed by the feature network. Instead, they are propagated by a flow network $ N_{flow} $.  Zhu, Xiong, Dai, Yuan and Wei use a state-of-the-art CNN based FlowNet architecture as a flow network. The flow estimation is given by: \newline

@@

$ f_{k} $ is the key frame's feature map, $ M_{i->k} $ is a two dimensional flow field, it projects back the location of an object in the current frame to the location in the key frame by using bilinear interpolation and  $ S_{i->k} $ is scale field. \newline

>>>>

\begin{figure} [h]
\includegraphics[width=\columnwidth]{RMFSSD}
\caption{Architecture: Recurent Multi-frame single shot detector [1]. The Feature Extractor generates feature maps for four frames and feeds those feature maps into the GRUs (Gated Recurrent Units). The Detection Head uses the final feature maps which are created by the GRU with respect to the temporal context to create Bounding Boxes and Class probabilities}
\end{figure}

In addition Broad, Jones and Lee test different types of SSDs as a baseline for their architecture. For all baseline SSDs the mAP was higher in comparison to the non-recurrent models. The mAP increase by 1.4 to 4.4 percent on KITTI dataset.  The best mAP is achieved using SqueezeDet+ \cite{b23} as a baseline SSD network [1-4.2].  \newline

@@

Afterwards, they compare LSTMs, GRUs and Bottleneck LSTMs by placing them after the 13th convolutional layer. Bottleneck-LSTMs have been designed by Liu and Zhu to increase the efficiency of LSTMs. They use convolutions with ReLU as activation function and feed Bottleneck feature map with less input channel then the original feature map into the LST. They come to the conclusion that Bottleneck-LSTMs are more effective the LSTMs and in the case of a convolutional kernel greater 1x1 even more effective than GRUs while attaining comparable perfomance. [2-3.4; 2-4.2]\newline

@@

As shown in Fig. 2 the final model uses LSTMs after each convolutional Layer, because Liu and Zhu observe that there is a slight performance improve by adding LSTMs after every feature map and nearly no change in computational cost [2-4.2].

\begin{figure} [h]
\includegraphics[width=\columnwidth]{Liu_Zhu}
\caption{Architecture Mobile Video Object Detection with temporally aware feature maps \cite{b2}. First 13 Convolutional Layeer create Feature Maps. Those Feature Maps are fed into the convolutional Bottleneck-LSTMs (faster LSTMs which use convolutions). Afterwards Convolutional-Layer create new Feature Maps and feed them again into Bottleneck-LSTMs.}
\end{figure}

@@

\subsection{Context Matters: Refining Object Detection in Video with Recurrent Neural Networks \cite{b4}}
In \cite{b4} Tripathi's, Lipton's, Belongie's and Nguyen's architecture consists two parts: A pseudo-labeler, which assigns labels to all video frames and a recurrent unit which refines those pseudo-labels by using the contextual information. Moreover, they describe a training strategy for their architecture and compare their approach to other models on the YouTube-Objects dataset (v2.0) \cite{b25} , which consists of the ten categories airplane, bird, boat, car, cow, dog, horse, mbike, train. Their model reaches an mAP of 68.73 percent which improves the strongest image-based baseline for Youtube-Video Objects dataset of 7.1\% [4-Abstract]. \newline

@@

\begin{figure} [h]
\includegraphics[width=\columnwidth]{ContextMatters}
\caption{Architecture Context Matters: Refining Object Detection in Video with Recurrent Neural Networks \cite{b4}. First the "Pseudolabler" creates bounding boxes and class probabilities for every input frame. Afterwards the GRU (Gated Recurrent Unit) fuses the output of the current and some past frames and refines the bounding boxes and class probabilities.}
\end{figure}

@@

\subsection{Spatially Supervised Recurrent Convolutional Neural Networks for Visual Object Tracking \cite{b5}}
Ning, Zhang, Huang, He, Ren and Wang design in \cite{b5} a combination of box-level and feature-level based Video detectors. They use the YOLO \cite{b26} network to create high-level visual features and preliminary location inferences and feed both into a recurrent unit. They test their approach on the OTB-30 dataset \cite{b28} and compared it with 9 different state-of-the-art trackers and outperform all of them. Their architecture, called ROLO, is shown in figure 11. [5-Abstract; 5-4]

@@

The architecture consists two main parts. The YOLO \cite{26} networks which collects visual features and outputs also preliminary location inferences and the LSTM which is used as a tracking module [5-2]. \newline

@@

In the pre-training phase convolutional layers, which create feature maps are pretrained on ImageNet data. Afterwards the YOLO-architecture is adopted as detection module and trained by using the traditional YOLO training phase. Lastly they add LSTMs for tracking. The LSTMs are fed with, the feature representations from the convolutional layers, the Bounding boxes from the detection module and the output states from the LSTM in the previous time-step. For training they use the Mean Squared Error (MSE) [5-3]: \newline

@@

In 2015 Wu, Lim and Yang published a comparison of different online object trackers on their one data set \cite{b28}. The best 9 architectures (STRUCK [47]; CXT [48]; OAB [49]; CSK [50]; VTD [51]; VTS [52]; LSK [53]; TLD [54]; RS [55]) were used by Ning, Zhang, Huang, He, Ren and Wang to compare them with their own architecture. They use 30 videos with different objects (e.g.: car, human, Skater, Couple,..) out of the benchmark \cite{b28} dataset. They get the best tracking result in 13 videos and the second best in 3 videos. There is no other tracker that reaches the best results in more then 4 videos. \newline

@@

\subsection{Deep Feature Flow for Video Recognition \cite{b3}}
Zhu, Xiong, Dai, Yuan and Wei develop in \cite{b2} a way to use flow nets to detect objects in video frames. As shown in figure 10 their architecture consists of three main parts: A network to create visual features, a network to create class probabilities and bounding boxes respectively the segmentation out of feature maps, and a network which estimates the optical flow. They tested their approach on the Cityscapes dataset \cite{b56}  with scenes for autonomous driving and ground-truth for semantic segmentation and the ImageNet VID dataset \cite{b35} with ground truth for object detection.

\begin{figure} [h]
\includegraphics[width=\columnwidth]{Flow}
\caption{Architecture Deep Feature Flow for Video Recognition \cite{b3}. The feature Network $N_{feat}$ extracts visual features for the key frames. The $N_{task}$ networks uses visual features to create Bounding boxes and Class probabilities. For non-key frame images, the flow networks F estimates the feature maps based on in a image sequence.} 
\end{figure}

The paper differs between key frames and other frames. The network to create visual features $ N_{feat} $ only processes on key frames. It is a fully convolutional network, which takes as an input the image and outputs a feature maps. As a feature network they use a pretrained version of ResNet. [3-3, 3-4] \newline

The second network $ N_{task} $ does the recognition task over the feature maps. It performs on every frame.  Zhu, Xiong, Dai, Yuan and Wei use an R-FCN \cite{b19} network for the recognition task. [3-3, 3-4]  \newline

For all non-key frames the feature maps are not constructed by the feature network. Instead, they are propagated by a flow network $ N_{flow} $.  Zhu, Xiong, Dai, Yuan and Wei use a state-of-the-art CNN based FlowNet architecture \cite{b57} as a flow network. The flow estimation is given by [3-3, 3-4]: \newline

@@

$ f_{k} $ is the key frame's feature map, $ M_{i->k} $ is a two dimensional flow field, it projects back the location of an object in the current frame to the location in the key frame by using bilinear interpolation and  $ S_{i->k} $ is scale field [3-3]. \newline
